Classless Java

### 2015-11-11 paper/paper.tex
more related work
Some work on comparision and related work. Section Future work now exists
Abstract first draft

@@

\input{sections/Compare.tex}

>>>>

Java 8 introduced \emph{default methods}, allowing interfaces to
have method implementations. When combined with (multiple) interface
inheritance, default methods provide a basic form of multiple
inheritance. However, using this combination to simulate multiple
inheritance quickly becomes cumbersome, and appears to be quite
restricted.

This paper shows that, with some minor syntactic sugar, default
methods and interface inheritance are in fact be very expressive. Our
proposed syntax sugar, called \emph{concrete interfaces}, enables
powerful object-oriented idioms, using multiple inheritance, to be
expressed directly in Java. Concrete interfaces avoid some syntactic
boilerplate caused by Java being originally designed to work mainly
with classes. Moreover, concrete interfaces come with their own object
instantiation mechanism, providing an alternative to class
constructors. As a result many Java programs can be built without
using a single class! An implementation of concrete interfaces using 
Java annotations and a formalization of the static and dynamic
semantics are presented. Moreover the usefulness of concrete
interfaces is illustrated through various examples and case studies.
\bruno{a first draft of the abstract. still missing ``lightweight
  language extensions''.}

@@
